
\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{geometry}
\geometry{a4paper}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{csquotes}
\usepackage{epigraph}
\usepackage{multicol}
\usepackage{enumerate}% http://ctan.org/pkg/enumerate
\usepackage{listings}
\usepackage{xcolor}
\usepackage{pythonhighlight}

\begin{document}
\author{\textbf{Fractals Community}}
\title{\textsc{Fractulum Mathathon}}
\maketitle

\epigraph{God made the natural numbers; all else is the work of man.}{Leopold Kronecker}

\begin{enumerate}
    \item
Given two integers, define an operation $*$ such that if $a$ and $b$ are integers, then $a*b$ is an integer.
The operation $*$ has the following properties:
\begin{itemize}
    \item $a*a = 0$ for all integers $a$;
    \item $(ka+b)*a = b* a$ for all integers $a$, $b$, and $k$;
    \item $0 \leq b*a < a$.
    \item $0 \leq b < a$ then $b*a = b$.
\end{itemize}
Find $2021 * 16$



\item It’s currently $6:00$ on a $12$ hour clock. What time will be shown on the clock $100$ hours from
now? Express your answer in the form $hh : mm$.


\item We call a positive integer \textit{binary-okay} if at least half of the digits in its binary (base 2) representation are 1’s, but no two 1s are consecutive. For example, $10_{10} = 1010_2$ and $5_{10} = 101_2$
are both binary-okay, but $16_{10} = {10000}_2$ and $11_{10} = {1011}_2$ are not. Compute the number of
binary-okay positive integers less than or equal to $2021$ (in base $10$).


\item Let $n$ be an integer such that $n^4 -2n^3 -n^2 +2n + 2$ is a prime number. What's the sum
of all possible $n$?


\item Find the number of subsets $S$ of $\{1,2,...,10\}$ such that no two of the elements in $S$ are consecutive

\item Can an $8\times8$ board be coverd by $15$ $1\times4$ rectangles and only one $2\times2$ square without overlaping? prove your answer.


\newpage
\item A $3  \times 3$ magic square is a grid of distinct numbers whose rows, columns, and diagonals
all add to the same integer sum. Connie creates a magic square whose sum is $N$, but her
keyboard is broken so that when she types a number, one of the digits ($0 - 9$) always appears
as a different digit (e.g. if the digit $8$ always appears as $5$, the number $18$ will appear as $15$).
The altered square is shown below. Find $N$.

\begin{table}[h]
    \begin{center}

\begin{tabular}{|l|l|l|}
\hline
9  & 11 & 10 \\ \hline
18 & 17 & 6  \\ \hline
14 & 11 & 15 \\ \hline
\end{tabular}
\end{center}
\end{table}
\item Compute
$$\sum_{k \ge 0} {1000 \choose 3k}$$
\end{enumerate}

% \begin{center}
%     End of Probems
% \end{center}
\leavevmode
$\pi \pi \pi   \pi\pi \pi \pi \pi \pi \pi\pi \pi
\pi \pi \pi \pi \pi \pi\pi \pi \pi \pi \pi \pi\pi \pi \pi \pi \pi
$ End of Problems
$\pi \pi \pi   \pi\pi \pi \pi \pi \pi \pi\pi \pi
\pi \pi \pi \pi \pi \pi\pi \pi \pi \pi \pi \pi\pi \pi \pi \pi \pi$
\newline
\leavevmode
\newline
\newline
\newline
\newline
\newline
% \newline
\begin{python}
>>> from engineering.math import pi, e
>>> pi == e
True
\end{python}
\end{document}
